---
title: "Merger simulation"
author: "Junjun Zhang"
date: "2022/5/9"
output:
  html_document: default
  pdf_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = F,message = F)
```



```{r,include=TRUE}
# Check  whether the packages called below require installation.
rm (list = ls(all=TRUE))#Clearn objects from the workspace
graphics.off() #Close the graphics
#Simple, Consistent Wrappers for Common String Operations
if ('stringr' %in% rownames(installed.packages())==FALSE) {
  install.packages('stringr')
}else{
  library(stringr)
}
#Extract this Rmd file's working directory
if (!'rstudioapi' %in% rownames(installed.packages())) {
  install.packages('rstudioapi')
}else{
  library(rstudioapi)
}
#Export the regression result to xlsx
if ('openxlsx' %in% rownames(installed.packages())==FALSE) {
  install.packages('openxlsx')
}else{
  library(openxlsx)
}

#Export the regression result to latex format tables
if (!'stargazer' %in% rownames(installed.packages())) {
  install.packages('stargazer')
}else{
  library(stargazer)
}
#Connect to pyblp python package
if (!'reticulate' %in% rownames(installed.packages())) {
  install.packages('reticulate')
}else{
  library(reticulate)
}
#Visulaize the missing values in the dataframe
if (!'VIM' %in% rownames(installed.packages())) {
  install.packages('VIM')
}else{
  library(VIM)
}
#  A Grammar of Data Manipulation
if (!'dplyr' %in% rownames(installed.packages())) {
  install.packages('dplyr')
}else{
  library(dplyr)
}
#Fast and User-Friendly Fixed-Effects Estimations
if (!'fixest' %in% rownames(installed.packages())) {
  install.packages('fixest')
}else{
  library(fixest)
}
#Package for 2sls regression
if (!'ivreg' %in% rownames(installed.packages())) {
  install.packages('ivreg')
}else{
  library(ivreg)
}


```

# Set the working directory
```{r analysis,include=TRUE}
script_path <- rstudioapi::getActiveDocumentContext()$path
hash = "(.*)/"
setwd(str_extract(script_path, hash)) 
```

```{r}
data1 <- readRDS('../data/Rds_data/complete_data2.Rds')#read the data
data1 <- data1[,-c(5,8)] #delete the title and sales column
prochar <- read.csv('../data/raw_char.csv')#Read product characteristics data 
#select the suction,battery life,package dimension,item-weight
# Check the NA,NAN and NULL value, due to limitation of collecting from Amazon
prochar1 <- prochar[!is.na(prochar$Wok_1charge),]
prochar2 <- prochar1[!is.na(prochar1$suction),]
prochar2 <- prochar2[!is.na(prochar2$ProDim),]
prochar2 <- prochar2[!is.na(prochar2$Item_Weight),]
prochar3 <- prochar2[!is.null(prochar2$Wok_1charge),]
prochar3 <- prochar2[!is.null(prochar2$suction),]
# Take out the suction,work_1charge, prodim and item weight,type1 and asin columns
prochar4 <- prochar3[,c(2,3,7,10,12,13)] 
#Merge the data with the characteristics data
data2 <- data1[data1$asin %in% prochar4$asin,]
data3 <- merge(data2,prochar4,by='asin')

# Convert the product dimension data into length x width x height numerical data
kk <- data3$ProDim
kk <- gsub('\\s','',kk)
ttttt <- str_split(kk,'x')
number_vector <- c()
for (i in seq(1,length(ttttt),1)) {
  FOR_LOOP <- as.numeric(gsub('[A-Za-z]','',ttttt[[i]]))
  res <- 1
  if(length(FOR_LOOP)!=0){
    for (j in 1:length(FOR_LOOP)) {
      res <- res * FOR_LOOP[j]
    }
  }
  
  number_vector <- append(number_vector,res)
  
}
data3$ProDim <- number_vector
data3$Item_Weight <- as.numeric(gsub('[A-Za-z]','',data3$Item_Weight)) # Clean the item-weight data

```

# Prepare the data
##  Visualize the missing values
```{r  check the missing valuables}
data4 <- data3
summary(data4)
stargazer(data4,summary = TRUE)
# aggr(data4,prop=FALSE,numbers=TRUE,cex.axis=0.6,ylabs = c('Number of missing values','Combinations'))
```




```{r  blp IV}
# Ownership structure function
owner <- function(thisOwner){
  owners <- as.numeric(factor(thisOwner, levels= unique(thisOwner)))
  nprod <- length(thisOwner)
  thisOwner <- matrix(0,ncol=nprod,nrow=nprod)
  for( o in unique(owners)){
    thisOwner [owners == o, owners == o] = 1
  }
  return(thisOwner)
}
## Prepare for the regression, clear the missing value here
data4 <- data4[!is.na(data3$prices),]
data4 <- data4[!is.nan(data3$prices),]
### Only choose there are more than ten products quarter data
table(data4$market_ids)      #we can see the number of product in market is increasing thought the time.
data4 <- data4[-which(data4$market_ids=='R16Q3',arr.ind = TRUE),]
data4 <- data4[-which(data4$market_ids=='R16Q4',arr.ind = TRUE),]
data4 <- data4[-which(data4$market_ids=='R17Q1',arr.ind = TRUE),]
data4 <- data4[-which(data4$market_ids=='R17Q2',arr.ind = TRUE),]
data4 <- data4[-which(data4$market_ids=='R17Q3',arr.ind = TRUE),]
data4 <- data4[-which(data4$market_ids=='R17Q4',arr.ind = TRUE),]

# Form the id for character value function
.indexing.markets <- function( cdidOld ) {
  cdidOld <- as.character(cdidOld)
  unique.ids <-  unique(cdidOld)
  nmkt <- length(unique.ids)
  cdid <- numeric(length(cdidOld))
  
  for(i in 1:nmkt ){
    relevantMarkets <- cdidOld == unique.ids[i]
    cdid[ relevantMarkets ] <- i
    
  }
  return( cdid )
}
#remember when you changed the iv, you need to re-index all the id data
# data4$firm_ids <- .indexing.markets(data4$brand)
# data4$product_ids <- .indexing.markets(data4$asin)
data4$pro_age <- 2022-as.numeric(data4$year)
data4 <- data4[complete.cases(data4$asin),]
data4$suction <- as.numeric(data4$suction)

# Redifine the product j here
# Now the definition of product j is based on the brand 
PROCESS <- data4 %>%
  group_by(market_ids,brand,type1) %>%
  summarise(Averate2 = mean(Averate2),
            prices = mean(prices),
            rating = sum(rating),
            shares = sum(shares),
            Wok_1charge = mean(Wok_1charge),
            suction = mean(suction),
            ProDim = mean(ProDim),
            Item_Weight = mean(Item_Weight),
            pro_age = mean(pro_age),
            num.pro = ifelse(n()>1,1,0)
  ) %>%
  ungroup()

PROCESS$firm_ids <- .indexing.markets(PROCESS$brand)
colnames(PROCESS)[2] <- 'Firm'
colnames(PROCESS)[3] <- 'brand'
PROCESS$product_ids <- .indexing.markets(PROCESS$brand)
coln <- colnames(PROCESS)
PROCESS <- as.data.frame(PROCESS)
colnames(PROCESS) <- coln
# cor(PROCESS[,c(4:12)])

#### Blp type iv function
constructIV <- function(firmid, cdid, id, X) {
  n <- dim(X)[1]
  p <- dim(X)[2]
  names <- colnames(X)
  if (is.null(names)) names <- paste("V", 1:p, sep="")
  sum.other <-  matrix(NA, nrow = n, ncol = p)
  colnames(sum.other) <- paste("sum.o.", names, sep="")  # sum other
  sum.rival <-  matrix(NA, nrow = n, ncol = p)
  colnames(sum.rival) <- paste("sum.r.", names, sep="")  # sum rival
  
  for (i in 1:n) {
    for (j in 1:p) {
      other_ind=(firmid==firmid[i] & cdid==cdid[i] & id!=id[i])
      rival_ind=(firmid!=firmid[i] & cdid==cdid[i])
      
      sum.other[i,j]=sum(X[other_ind==1,j])
      sum.rival[i,j]=sum(X[rival_ind==1,j]) 
    }
  }
  return(cbind(sum.other, sum.rival))
}
##work1charge,suction,item-weight,product dimension , and pro_age IV
blp_iv <- constructIV(PROCESS[,14],PROCESS[,1],PROCESS[,15],PROCESS[,8:12])
data5 <- cbind(PROCESS,blp_iv)
data5 <- data5[!is.na(data5$rating),]


```


```{r}
# Prepare for the regression data.
datatest <- data5
datatest$prices <- datatest$prices/1000 # logit model, the price enters lineraly, while in CES, the price will enter logarithmly
datatest$shares <- log(datatest$shares)-log(0.5) ## Do I need to line up the same form as the estimation form, what is the quatity  and income in my model.

# stargazer(datatest)

####  Firm id dummy and Market id dummy
dummycol <- data.frame(datatest$product_ids)
colnames(dummycol) <- c("product")
#Package for dummy variables
if (!'fastDummies' %in% rownames(installed.packages())) {
  install.packages('fastDummies')
}else{
  library(fastDummies)
}
test.df <- dummy_cols(dummycol, select_columns = "product", remove_first_dummy = T)
test.df <- test.df[,-1]
datatest2 <- cbind(datatest, test.df)

#quarter fixed effect
dummycol_time <- data.frame(datatest$market_ids)
colnames(dummycol_time) <- c("quarYear")

test.df_time <- dummy_cols(dummycol_time, select_columns = "quarYear", remove_first_dummy = T)
test.df_time1 <- test.df_time[,-1]
datatest2 <- cbind(datatest2, test.df_time1)

#First stage  12:157,158:173,174:176,177:192
stage1_price <- lm(prices~ .-shares -Averate2,data = datatest2[,-c(1:3,6,14:15,26:187)])
# summary(stage1_price)

stage1_quality <- lm(Averate2~ .-prices -shares,data = datatest2[,-c(1:3,6,14:15,26:187)])
# summary(stage1_quality)

names <- tibble(test.df,test.df_time1)
name <- colnames(names)
stargazer(stage1_price,stage1_quality,omit =name )

# ols
m_ols <- lm(shares ~ .,data =datatest2[,-c(1:3,6,14:15)] )
test1 <- datatest2[,-c(1:3,6,10,14:15,18,21:25)]
#Based on first stage regression result, we use sum.o.Wok_1charge ,sum.o.suction and sum.o.pro_age as IVS
m_iv_put <- ivreg(shares ~ .-sum.o.Wok_1charge -sum.o.suction  -sum.o.pro_age |  .-prices -Averate2, data = test1[,-11])
# summary(m_iv_put)

#Show the regression result of OLS and 2SLS
stargazer(m_ols,m_iv_put,title="Regression Results",omit = name,type = 'text')

alpha <- -1.034  # get from the 2sls regression result. Coefficient of price
tau <- 0.3667# Coefficient of quality g
# Get the innitail meanvalue vector
value <- m_iv_put$fitted.values- alpha * datatest2$prices- tau * datatest2$Averate2
datatest4 <-datatest2
datatest4$meanval <- value 
#Create a working environment to store data into excel file
wb1 <- createWorkbook(creator = 'junjunz',title = 'ces_d')

```


$$
U_{ijt}=\alpha p_{jt}+\tau g_{jt} + x_{jt}\beta + \xi_{jt}+\epsilon_{ijt}
$$


The $i$ is the consumer.The $j$ is the product, and $t$ is the market which is expressed as  quarter.The price and quality of the product are $p_{jt}$ and $g_{jt}$ which are endogenous variable in my model. The $x_{jt}$ are the demand side exogenous product characteristics and the control variables. $\beta$ is the coefficient of exogenous product characteristics. $\xi_{jt}$ is unobserved demand side product characteristics.The utility of the outside goods is usual normalized to zero($U_{i0t}=\epsilon_{i0t}$). $\epsilon_{ijt}$ is distributed IID with the Type I Extreme value distribution. The market share can be  as following

$$
s_{jt} = \frac{exp(\alpha p_{jt}+\tau g_{jt} + x_{jt}\beta + \xi_{jt})}{1 + \sum_{k}^{J}exp(\alpha p_{kt}+\tau g_{kt} + x_{kt}\beta + \xi_{kt})}
$$
Take the log of the above equation, we get:
$$
log(s_{jt})=\alpha p_{jt}+\tau g_{jt} + x_{jt}\beta + \xi_{jt}-log(\sum_{k}^{J}exp(\alpha p_{kt}+\tau g_{kt} + x_{kt}\beta + \xi_{kt}))
$$
and 

$$
log(s_{0t})=-log(\sum_{k}^{J}exp(\alpha p_{kt}+\tau g_{kt} + x_{kt}\beta^{ex} + \xi_{kt}))
$$
The differEnce between the two equations is:
$$
log(s_{jt})-log(s_{0t})=\alpha p_{jt}+\tau g_{jt} + x_{jt}\beta + \xi_{jt}
$$
$s_{jt}$ is the market share of product $j$ and $s_{0t}$ is the market share of the outside goods which is assumed as 0.5 in my case. Then we estimate the above equation by IV GMM. The total number of product in each market is $J$.

### Run the merger simulation

I set the meanval which is $x_{kt}\beta + \xi_{kt}$ to be a fixed vector. I  extract one market data which is R22Q1 market to do the merger simulation.




Function owner is the ownership structure function

```{r ownershiip}
owner <- function(thisOwner){
  owners <- as.numeric(factor(thisOwner, levels= unique(thisOwner)))
  nprod <- length(thisOwner)
  thisOwner <- matrix(0,ncol=nprod,nrow=nprod)
  for( o in unique(owners)){
    thisOwner [owners == o, owners == o] = 1
  }
  return(thisOwner)
}
```


## Claculate the market shares 
The market shares are calculated using the following equation:

$$
s_{jt} = \frac{exp(\alpha p_{jt}+\tau g_{jt} + x_{jt}\beta + \xi_{jt})}{1 + \sum_{k}^{J}exp(\alpha p_{kt}+\tau g_{kt} + x_{kt}\beta + \xi_{kt})}
$$

The $g_{jT}$ is the quality of product j in market t which is expressed as the average number of ratings. $p_{jt}$ is the price of the product j in market t. Here I will set a initial variable for  $ x_{j}\beta+ \xi_{j}$ which is meanval in the code.Here I assume only the price $p_{jt}$ and quality level $g_{jt}$ will change. So in the later code, I am trying to find the fixed point of the price and quality level. 

Function calcShares is the calculation of market share.
```{r market shares}
#Market shares function when price and quality change at the same time
calcShares <- function(prices,quality,meanval,alpha,tau){
  shares <- exp(meanval + alpha*prices+tau*quality)
  shares <- shares/(1 + sum(shares,na.rm=TRUE))
  return(shares)
}

#Market shares function when price only changes
calcShares.p <- function(prices,quality,meanval,alpha,tau){
  shares <- exp(meanval + alpha*prices+tau*quality)
  shares <- shares/(1 + sum(shares,na.rm=TRUE))
  return(shares)
}



```


## Calculate the elasticities

Calculate the price elasticity of the product according to 
$$
    \eta_{jk} = \frac{\partial s_{j}}{\partial p_{k} }\frac{ p_{k}}{ s_{j}}=\{ \begin{array}{rcl}
    \alpha (1-s_{j})p_{k}      &      & {if\quad j=k}\\
    -\alpha s_{k}p_{k}     &      & {otherwise}\\
    \end{array}
$$

```{r}
elast_price <- function(shares,prices,alpha){
  nprods <-  length(shares)
  shares <- as.matrix(shares,nrow = nprods, ncol = 1)
  elast <- -alpha  * matrix(prices*shares,ncol=nprods,nrow=nprods,byrow=TRUE)
  diag(elast) <- alpha*prices + diag(elast)
  return(elast)
}
```


## Calculate the quality elasticities
The elasticity of quality will be calculated as follows:
$$
    \psi_{jk} = \frac{\partial s_{j}}{\partial g_{k} }\frac{ g_{k}}{ s_{j}}=\{ \begin{array}{rcl}
    \tau (1-s_{j})g_{k}      &      & {if\quad j=k}\\
    -\tau g_{k}s_{k}     &      & {otherwise}\\
    \end{array}
$$

```{r quality}
elast_quality <- function(shares,quality,tau){
  nprods <-  length(shares)
  shares <- as.matrix(shares,nrow = nprods, ncol = 1)
  elast <- -tau  * matrix(quality*shares,ncol=nprods,nrow=nprods,byrow=TRUE)
  diag(elast) <- tau*quality + diag(elast)
  return(elast)
}
```

## Calculate the marginal cost of quality

Calculate the marginal cost according to,
$$
    \pi_{f}(\boldsymbol{p} ,\boldsymbol{g}) = \sum_{k\in \mathcal{F}_f}((p_{k}-c_{k}+\delta)q_k(\boldsymbol{p} ,\boldsymbol{g}) - C(g_k)) 
$$




Where $p_{k}$ is the price of product $j$. $c_{k}$ is the constant marginal cost of product $k$. $q_j(\boldsymbol{p} ,\boldsymbol{g})$ is demand,as given by 1, now written as a function of the $J\; \times \;1$ price vector $\boldsymbol{p}$ and quality vector $\boldsymbol{g}$.  $\delta$ is the product efficiency which is assumed constant. $C(g_{k})$ is the cost of investment on product k which is assumed convex and increasing.The profit-maximizing price of each product $j=1,\cdots ,J$ should satisfy the following first-order condition:
$$
        q_{j}(\boldsymbol{p},\boldsymbol{g}) + \sum_{k\in \mathcal{F}_f}(p_{k}-c_{k}+\delta) \frac{\partial q_{k}(\boldsymbol{p},\boldsymbol{g})}{\partial p_{j}}=0  
$$

And it can be inverted into the following expression:
$$
\boldsymbol{c=p+(\Omega^{F} \odot \bigtriangleup(p))^{-1}q(p,g)}
$$
The markup on the right hand is determined by demand's own-price and cross-price elasticities.


The marginal cost$c$ can be calculated using premerger prices and estimated demand price elasticities:
$$
\boldsymbol{c^{pre}=p^{pre}+(\Omega^{F,pre} \odot \Delta(p^{pre}))^{-1}s(p^{pre})}
$$

The above equation can be changed in two ways. One is the change in ownership as a result of the merger; another is the marginal cost ( I assume the marginal cost will not change in this model). Later, I'll use the fixed point iteration to solve the nonlinear system equation.

$\Omega^{F} \odot \Delta(p)$ is the product ownership structure multiply partial derivatives which can be expressed as following:

In logit, the quatity should equal the market share.

$$
\Omega^{pre}\odot \Delta(p^{pre})=\left\{
\begin{array}{cccccc}
\frac{\partial s_{1}}{\partial p_{1}}(p^{pre},g^{pre}) \cdot \Omega_{1,1} & \frac{\partial s_{2}}{\partial p_{1}}(p^{pre},g^{pre}) \cdot \Omega_{1,2} &\cdots&\frac{\partial s_{j}}{\partial p_{1}}(p^{pre},g^{pre}) \cdot \Omega_{1,j} & \cdots&\frac{\partial s_{J}}{\partial p_{1}}(p^{pre},g^{pre}) \cdot \Omega_{1,J}\\
\frac{\partial s_{1}}{\partial p_{2}}(p^{pre},g^{pre}) \cdot \Omega_{2,1} & \frac{\partial s_{2}}{\partial p_{2}}(p^{pre},g^{pre}) \cdot \Omega_{2,2} &\cdots&\frac{\partial s_{j}}{\partial p_{2}}(p^{pre},g^{pre}) \cdot \Omega_{1,j} & \cdots&\frac{\partial D_{J}}{\partial p_{2}}(p^{pre},g^{pre}) \cdot \Omega_{2,J}\\
\vdots & \vdots & \ddots &  \vdots  &  \ddots   & \vdots \\
\frac{\partial s_{1}}{\partial p_{j}}(p^{pre},g^{pre}) \cdot \Omega_{k,1} & \frac{\partial s_{2}}{\partial p_{j}}(p^{pre},g^{pre}) \cdot \Omega_{k,2} &\cdots&\frac{\partial s_{j}}{\partial p_{j}}(p^{pre},g^{pre}) \cdot \Omega_{k,j} & \cdots&\frac{\partial s_{J}}{\partial p_{j}}(p^{pre},g^{pre}) \cdot \Omega_{k,J} \\
\vdots & \vdots & \ddots &  \vdots  &  \ddots   & \vdots \\
\frac{\partial s_{1}}{\partial p_{J}}(p^{pre},g^{pre}) \cdot \Omega_{J,1} & \frac{\partial s_{2}}{\partial p_{J}}(p^{pre},g^{pre}) \cdot \Omega_{J,2} &\cdots&\frac{\partial s_{j}}{\partial p_{J}}(p^{pre},g^{pre}) \cdot \Omega_{J,j} & \cdots&\frac{\partial s_{J}}{\partial p_{J}}(p^{pre},g^{pre}) \cdot \Omega_{J,J}
\end{array} \right \}     
$$


Where 

$$
\Omega_{k,j} = \left \{
\begin{array}{ccc}   
1 &  & \mbox{if product k and j are produced by the same firm}\\
0 &  & \mbox{otherwise}    
\end{array}    
\right.
$$

The partial derivatives $\frac{\partial s_{j}}{\partial p_{k}}$ is calculated based on the elasticity $\eta_{jk} = \frac{\partial s_{j}}{\partial p_{k} }\frac{ p_{k}}{ s_{j}}$, then

$$
\frac{\partial s_{j}}{\partial p_{k}}=\eta_{jk}\cdot\frac{s_{j}}{ p_{k}}
$$


```{r}
calcMc_price <- function(prices,quality,meanval,alpha,tau,owner){
  share_i <- calcShares(prices,quality,meanval,alpha,tau)
  price_over_share_i <- matrix(1/(share_i)) %*% matrix(prices, nrow = 1)
  elasticities_i <- elast_price(share_i,prices,alpha)
  derivatives_i <- elasticities_i / price_over_share_i # partial derivatives of shares wrt price
  own_prod_pre_i <- owner # if element (i,j) equals 1, that means that prod i and j are produced by same firm
  markups <- c(solve(t(derivatives_i) * own_prod_pre_i) %*% (share_i))
  arg_cost <- prices + markups
  isNegMC <- arg_cost < 0
  if(any(isNegMC, na.rm = TRUE)){
    # warning(paste("Negative marginal costs were calibrated for the following brands:", paste(prodNames[isNegMC], collapse=",")))
    arg_cost[isNegMC] <- min(arg_cost[!isNegMC]) #set the negative marginal cost to the lowest positive vaule in the data
  }
  return(arg_cost)
}
```

## Estimate the marginal cost of the investment
First I will get the initial $C^{'}_{g}$ according to the following equation:
$$
    \boldsymbol{(\Omega^{pre} \odot \Delta(g^{pre}))(p^{pre}-c^{pre}) =C^{'pre}(g_{k})}
$$
$\Omega^{pre}$ is the product ownership structure. $\Delta(g^{pre})$ is the partial derivative with respect to quality($g$). $C^{'pre}(g_{k})$ is the marginal cost of quality($g_{k}$). Then $\Omega^{pre} \odot \Delta(g^{pre})$ can be expressed as following:

$$
\Omega^{pre} \odot \Delta(g^{pre})=\left\{
\begin{array}{cccccc}
\frac{\partial s_{1}}{\partial g_{1}}(p^{pre},g^{pre}) \cdot \Omega_{1,1} & \frac{\partial s_{2}}{\partial g_{1}}(p^{pre},g^{pre}) \cdot \Omega_{1,2} &\cdots&\frac{\partial s_{j}}{\partial g_{1}}(p^{pre},g^{pre}) \cdot \Omega_{1,j} & \cdots&\frac{\partial s_{J}}{\partial g_{1}}(p^{pre},g^{pre}) \cdot \Omega_{1,J}\\
\frac{\partial s_{1}}{\partial g_{2}}(p^{pre},g^{pre}) \cdot \Omega_{2,1} & \frac{\partial s_{2}}{\partial g_{2}}(p^{pre},g^{pre}) \cdot \Omega_{2,2} &\cdots&\frac{\partial s_{j}}{\partial g_{2}}(p^{pre},g^{pre}) \cdot \Omega_{1,j} & \cdots&\frac{\partial s_{J}}{\partial g_{2}}(p^{pre},g^{pre}) \cdot \Omega_{2,J}\\
\vdots & \vdots & \ddots &  \vdots  &  \ddots   & \vdots \\
\frac{\partial s_{1}}{\partial g_{j}}(p^{pre},g^{pre}) \cdot \Omega_{k,1} & \frac{\partial s_{2}}{\partial g_{j}}(p^{pre},g^{pre}) \cdot \Omega_{k,2} &\cdots&\frac{\partial s_{j}}{\partial p_{j}}(p^{pre},g^{pre}) \cdot \Omega_{k,j} & \cdots&\frac{\partial s_{J}}{\partial g_{j}}(p^{pre},g^{pre}) \cdot \Omega_{k,J} \\
\vdots & \vdots & \ddots &  \vdots  &  \ddots   & \vdots \\
\frac{\partial s_{1}}{\partial g_{J}}(p^{pre},g^{pre}) \cdot \Omega_{J,1} & \frac{\partial s_{2}}{\partial g_{J}}(p^{pre},g^{pre}) \cdot \Omega_{J,2} &\cdots&\frac{\partial s_{j}}{\partial p_{J}}(p^{pre},g^{pre}) \cdot \Omega_{J,j} & \cdots&\frac{\partial s_{J}}{\partial g_{J}}(p^{pre},g^{pre}) \cdot \Omega_{J,J}
\end{array} \right \} 
$$


Where 

$$
\Omega_{k,j} = \left \{
\begin{array}{ccc}
1 &  & \mbox{if product k and j are produced by the same firm}\\
0 &  & \mbox{otherwise}
\end{array} 
\right.
$$


This is the function for calculating the  marginal cost of investment $C^{'}(g)$.

```{r}
calcMC_quality <- function(prices,quality,meanval,alpha,tau,owner){
  mc_price <- calcMc_price(prices,quality,meanval,alpha,tau,owner)
  share_i <- calcShares(prices,quality,meanval,alpha,tau)
  quality_pre_i <- quality
  quality_over_share_i <- matrix(1 / (share_i)) %*% matrix(quality_pre_i, nrow = 1)
  elasticities_i <- elast_quality(share_i,quality_pre_i,tau)
  derivatives_i <- elasticities_i / quality_over_share_i # partial derivatives of shares wrt quality
  own_prod_pre_i <- owner # if element (i,j) equals 1, that means that prod i and j are produced by same firm
  mc_quality <- (t(derivatives_i) * own_prod_pre_i) %*% (prices-mc_price)
  isNegMC <- mc_quality < 0
  
  if(any(isNegMC, na.rm = TRUE)){
    mc_quality[isNegMC] <- min(mc_quality[!isNegMC])#set the negative marginal cost to the lowest positive vaule in the data

    }
  return(mc_quality)
}

```

Calculate the shares and marginal cost when only the price changes.
```{r}
calcShares.p <- function(prices,quality,meanval,alpha,tau){
  shares <- exp(meanval + alpha*prices+tau*quality)
  shares <- shares/(1 + sum(shares,na.rm=TRUE))
  return(shares)
}


calcMc_price.p <- function(prices,quality,meanval,alpha,tau,owner){
  share_i <- calcShares.p(prices,quality,meanval,alpha,tau)
  price_over_share_i <- matrix(1 / (share_i)) %*% matrix(prices, nrow = 1)
  elasticities_i <- elast_price(share_i,prices,alpha)
  derivatives_i <- elasticities_i / price_over_share_i # partial derivatives of shares wrt price
  own_prod_pre_i <- owner # if element (i,j) equals 1, that means that prod i and j are produced by same firm
  markups <- c(solve(t(derivatives_i) * own_prod_pre_i) %*% (share_i))
  arg_cost <- prices + markups
  isNegMC <- arg_cost < 0

  if(any(isNegMC, na.rm = TRUE)){
    # warning(paste("Negative marginal costs were calibrated for the following brands:", paste(prodNames[isNegMC], collapse=",")))
    arg_cost[isNegMC] <- min(arg_cost[!isNegMC])
  }
  return(arg_cost)
}
```



I suppose that the quality's marginal cost can be stated as a linear form of quality. Then I run the following basic regression:

$$
C^{'} = a+\beta g + \epsilon
$$




```{r HHHHHHHHHHHHHHHHHHHHHHHHHHHHHHH}
datatest5 <- datatest4
meanval <- datatest5$meanval
quality_pre <- datatest5$Averate2 # The average of ratings are expressed as the product quality
price_pre <-datatest5$prices
brand_pre <- datatest5$Firm
ownerpre <- owner(brand_pre)
datatest5$Firm[which(datatest5$Firm=='ilife')] = 'irobot'
brand_post <- datatest5$Firm
ownerpost <- owner(brand_post)
mc.qua <- calcMC_quality(price_pre,quality_pre,meanval,alpha,tau,ownerpre)

datatest5$mc_quality_pre <- mc.qua
linear.2 <- feols(mc_quality_pre ~ Averate2| brand , datatest5)
coef_quality <- linear.2$coeftable[1,1]
etable(linear.2)
```

## Solve the nonlinear system equation by using BBsolve R package

Check the detail of the bbsolve R package(https://cran.r-project.org/web/packages/BB/index.html),

The fixed point of price and quality are calculated as following:

$$
\begin{pmatrix} \boldsymbol{s}  \\ \boldsymbol{-C_{g}^{'}}  \end{pmatrix}+\begin{pmatrix} \Omega \odot \Delta(p) & 0 \\ 0 & \Omega \odot \Delta(g) \end{pmatrix}\begin{pmatrix}  \boldsymbol{p-c} \\ \boldsymbol{p-c}  \end{pmatrix}=\begin{pmatrix} 0  \\ 0  \end{pmatrix}
$$

```{r}
set.seed(100)
# a loop for running the merger simulation based on the quater that you want to get
for (i in c('R20Q4','R21Q1','R21Q2','R21Q3','R21Q4','R22Q1')) {
  market_ids <- i
  data.R22Q1 <- datatest4[datatest4$market_ids==market_ids,]
  # meanval <- data.R22Q1$meanval
  # meanval <- rep(1,length(data.R22Q1$asin)) 
  ## Try to get 2020 to 2022
  # data.R22Q1$year <- as.numeric(data.R22Q1$year)
  prodNames <- data.R22Q1$asin # product label
 

  Unobpart <- datatest5$mc_quality_pre[datatest4$market_ids==market_ids]-linear.2$fitted.values[datatest4$market_ids==market_ids] # get the unobserved part that will affect the marginal cost of quality
  data.R22Q1$Unobpart <- Unobpart
  meanval <- data.R22Q1$meanval
  quality_pre <- data.R22Q1$Averate2 # The average of ratings are expressed as the product quality
  price_pre <-data.R22Q1$prices
  brand_pre <- data.R22Q1$Firm
  ownerpre <- owner(brand_pre)
  data.R22Q1$Firm[which(data.R22Q1$Firm=='ilife')] = 'irobot'
  brand_post <- data.R22Q1$Firm
  ownerpost <- owner(brand_post)
  data.R22Q1$Item_Weight <- as.numeric(data.R22Q1$Item_Weight)
  # L <- sum(data.R22Q1$rating)
  # L <- 1
  set.seed(100)
  # elasticities_pre_mkt <- elast_price()
  FOC <- function(innitial_vetor){
    len <- length(innitial_vetor)
    prices <- innitial_vetor[1:(len/2)]
    quality <- innitial_vetor[(len/2+1):len]
    implied_shares <- calcShares(prices,quality,meanval,alpha,tau)
    price_over_shares <- matrix(1 / (implied_shares)) %*% matrix(prices, nrow = 1)
    elasticities_pre_price <- elast_price(implied_shares,prices,alpha)
    derivatives_price <- elasticities_pre_price / price_over_shares
    
    # markups_post <- c(-solve(t(derivatives_price) * ownerpre) %*% implied_shares)
    marg_cost <- calcMc_price(price_pre,quality_pre,meanval,alpha,tau,ownerpre)
    
    quality_over_shares <- matrix(1 / (implied_shares)) %*% matrix(quality, nrow = 1)
    elasticities_pre_quality <- elast_quality(implied_shares,quality,tau)
    derivatives_quality <- elasticities_pre_quality / quality_over_shares
    
    # markups_post <- c(-solve(t(derivatives_quality) * ownerpre) %*% implied_shares)
    vec1 <- as.matrix(coef_quality*quality+Unobpart)
    M1_PRICE <- t(derivatives_price) * ownerpre
    M2_QUALITY <- t(derivatives_quality) * ownerpre
    Merge_matrix <- rbind(cbind(M1_PRICE,matrix(0,nrow=nrow(M1_PRICE),ncol=ncol(M2_QUALITY))),cbind(matrix(0,nrow=nrow(M2_QUALITY),ncol=ncol(M1_PRICE)),M2_QUALITY))
    price_mc <- prices - marg_cost
    matrix_price_mc <- append(price_mc,price_mc)
    matrix_price_mc <- matrix(matrix_price_mc,ncol = 1)
    matrix_shares_mC <- append((implied_shares),-vec1)
    matrix_shares_mC <- matrix(matrix_shares_mC,ncol = 1)
    thisFOC <- as.vector(matrix_shares_mC + Merge_matrix %*% matrix_price_mc)
    return(thisFOC)
  }
  
  #package for dummy variables
  
  if (!'BB' %in% rownames(installed.packages())) {
  install.packages('BB')
  }else{
  library(BB)
}
  
  innitial_vector <- append(data.R22Q1$prices,data.R22Q1$Averate2)
  minResult.pre <- dfsane(innitial_vector,FOC,quiet=FALSE,control=list(maxit = 5000))
  
  
  FOC_post <- function(innitial_vetor){
   
    len <- length(innitial_vetor)
    prices <- innitial_vetor[1:(len/2)]
    quality <- innitial_vetor[(len/2+1):len]
    implied_shares <- calcShares(prices,quality,meanval,alpha,tau)
    price_over_shares <- matrix(1 / (implied_shares)) %*% matrix(prices, nrow = 1)
    elasticities_pre_price <- elast_price(implied_shares,prices,alpha)
    derivatives_price <- elasticities_pre_price / price_over_shares
    
    # markups_post <- c(-solve(t(derivatives_price) * ownerpre) %*% implied_shares)
    marg_cost <- calcMc_price(price_pre,quality_pre,meanval,alpha,tau,ownerpre)
    
    quality_over_shares <- matrix(1 / (implied_shares)) %*% matrix(quality, nrow = 1)
    elasticities_pre_quality <- elast_quality(implied_shares,quality,tau)
    derivatives_quality <- elasticities_pre_quality / quality_over_shares
    
    # markups_post <- c(-solve(t(derivatives_quality) * ownerpre) %*% implied_shares)
    vec1 <- as.matrix(coef_quality*quality+Unobpart)
    # vec2 <- rep(1,length(quality))
    # vec1+vec2 <- calcMargins_quality(prices,quality)
    # f <- priceCand - marg_cost - markups_post
    # f <- priceCand - marg_cost - markups_post
    # f
    M1_PRICE <- t(derivatives_price) * ownerpost
    M2_QUALITY <- t(derivatives_quality) * ownerpost
    Merge_matrix <- rbind(cbind(M1_PRICE,matrix(0,nrow=nrow(M1_PRICE),ncol=ncol(M2_QUALITY))),cbind(matrix(0,nrow=nrow(M2_QUALITY),ncol=ncol(M1_PRICE)),M2_QUALITY))
    price_mc <- prices - marg_cost
    matrix_price_mc <- append(price_mc,price_mc)
    matrix_price_mc <- matrix(matrix_price_mc,ncol = 1)
    matrix_shares_mC <- append((implied_shares),-vec1)
    matrix_shares_mC <- matrix(matrix_shares_mC,ncol = 1)
    thisFOC <- as.vector(matrix_shares_mC + Merge_matrix %*% matrix_price_mc)
    return(thisFOC)
  }
  
  
  minResult.post <- dfsane(innitial_vector,FOC_post,quiet=FALSE,control=list(maxit = 5000))
  
  len <- length(innitial_vector)
  EstpricePre.pg <- minResult.pre$par[1:(len/2)]
  EstqualityPre.pg <- minResult.pre$par[(len/2+1):len]
  # EstqualityPre.pg[which(EstqualityPre.pg<0,arr.ind = T)] <- 0
  # EstqualityPre.pg[which(EstqualityPre.pg>5,arr.ind = T)] <- 5
  EstsharesPre.pg <- calcShares(EstpricePre.pg,EstqualityPre.pg,meanval,alpha,tau)
  EstpricePost.pg <- minResult.post$par[1:(len/2)]
  EstqualityPost.pg <- minResult.post$par[(len/2+1):len]
  # EstqualityPost.pg[which(EstqualityPost.pg<0,arr.ind = T)] <- 0
  # EstqualityPost.pg[which(EstqualityPost.pg>5,arr.ind = T)] <- 5
  EstsharesPost.pg <- calcShares(EstpricePost.pg,EstqualityPost.pg,meanval,alpha,tau)
  
  
  #pROPOSITION1
  #The l*m
  
  prices <- minResult.post$par[1:(len/2)]
  quality <- minResult.post$par[(len/2+1):len]
  implied_shares <- calcShares(prices,quality,meanval,alpha,tau)
  price_over_shares <- matrix(1 / (implied_shares)) %*% matrix(prices, nrow = 1)
  elasticities_pre_price <- elast_price(implied_shares,prices,alpha)
  derivatives_price <- elasticities_pre_price / price_over_shares
  
  quality_over_shares <- matrix(1 / (implied_shares)) %*% matrix(quality, nrow = 1)
  elasticities_pre_quality <- elast_quality(implied_shares,quality,tau)
  derivatives_quality <- elasticities_pre_quality / quality_over_shares
  
  p_diversion_ration <- -derivatives_price/diag(derivatives_price)
  p_diversion_ration.same <- p_diversion_ration * ownerpost
  price_ratio <- apply(p_diversion_ration.same,1,sum)
  
  q_diversion_ration <- -derivatives_quality/diag(derivatives_quality)
  q_diversion_ration.same <- q_diversion_ration * ownerpost 
  quality_ratio <- apply(q_diversion_ration.same,1,sum)
  
  quality_price_lm <- -quality_ratio/price_ratio*implied_shares
  
  #the h*m
  prices <- minResult.pre$par[1:(len/2)]
  quality <- minResult.pre$par[(len/2+1):len]
  implied_shares <- calcShares(prices,quality,meanval,alpha,tau)
  price_over_shares <- matrix(1 / (implied_shares)) %*% matrix(prices, nrow = 1)
  elasticities_pre_price <- elast_price(implied_shares,prices,alpha)
  derivatives_price <- elasticities_pre_price / price_over_shares
  
  quality_over_shares <- matrix(1 / (implied_shares)) %*% matrix(quality, nrow = 1)
  elasticities_pre_quality <- elast_quality(implied_shares,quality,tau)
  derivatives_quality <- elasticities_pre_quality / quality_over_shares
  
  
  
  
  quality_price_hm <- -diag(derivatives_quality)/diag(derivatives_price)*implied_shares
  
  lm_hm <- quality_price_lm - quality_price_hm
  
  g.m_g <- (EstqualityPost.pg- EstqualityPre.pg)/EstqualityPre.pg
  
  
  Est_result.pg <- data.frame(brand_pre,brand_post,EstpricePre.pg,EstqualityPre.pg,EstsharesPre.pg,EstpricePost.pg,
                              EstqualityPost.pg,EstsharesPost.pg,quality_price_lm,quality_price_hm,g.m_g,lm_hm)
  Est_result.pg$label <- ''
  Est_result.pg$label[Est_result.pg$brand_post=='irobot'] <- "*"
  Est_result.pg$priceDif.pg <- (Est_result.pg$EstpricePost-Est_result.pg$EstpricePre)/Est_result.pg$EstpricePre
  Est_result.pg$qualityDif.pg <- (Est_result.pg$EstqualityPost-Est_result.pg$EstqualityPre)/Est_result.pg$EstqualityPre
  Est_result.pg$EstsharDif.pg <- (Est_result.pg$EstsharesPost-Est_result.pg$EstsharesPre)/Est_result.pg$EstsharesPre
  Est_result.pg <- Est_result.pg %>%
    relocate(label,.after = brand_post)
  stargazer(Est_result.pg,type = 'text')
  

 
  
  
  FOC_p.pre <- function(innitial_vetor){
    len <- length(innitial_vetor)
    prices <- innitial_vetor[1:len]
    quality <- data.R22Q1$Averate2
    implied_shares <- calcShares.p(prices,quality,meanval,alpha,tau)
    price_over_shares <- matrix(1 / (implied_shares)) %*% matrix(prices, nrow = 1)
    elasticities_pre_price <- elast_price(implied_shares,prices,alpha)
    derivatives_price <- elasticities_pre_price / price_over_shares
    
    # markups_post <- c(-solve(t(derivatives_price) * ownerpre) %*% implied_shares)
    marg_cost <- calcMc_price.p(price_pre,quality_pre,meanval,alpha,tau,ownerpre)
    
    # quality_over_shares <- matrix(1 / implied_shares) %*% matrix(quality, nrow = 1)
    # elasticities_pre_quality <- elast_quality(implied_shares,quality)
    # derivatives_quality <- elasticities_pre_quality / quality_over_shares
    
    # markups_post <- c(-solve(t(derivatives_quality) * ownerpre) %*% implied_shares)
    # vec1 <- as.matrix(-0.4410*quality+Unobpart)
    M1_PRICE <- t(derivatives_price) * ownerpre
    # M2_QUALITY <- t(derivatives_quality) * ownerpre
    # Merge_matrix <- rbind(cbind(M1_PRICE,matrix(0,nrow=nrow(M1_PRICE),ncol=ncol(M2_QUALITY))),cbind(matrix(0,nrow=nrow(M2_QUALITY),ncol=ncol(M1_PRICE)),M2_QUALITY))
    price_mc <- prices - marg_cost
    # matrix_price_mc <- append(price_mc,price_mc)
    # matrix_price_mc <- matrix(matrix_price_mc,ncol = 1)
    # matrix_shares_mC <- append(implied_shares,-vec1)
    # matrix_shares_mC <- matrix(matrix_shares_mC,ncol = 1)
    thisFOC <- as.vector((implied_shares) + M1_PRICE %*% price_mc)
    return(thisFOC)
  }
  
  innitial_vector.p <- price_pre
  minResult.p.pre <- dfsane(innitial_vector.p,FOC_p.pre,quiet=FALSE,control=list(maxit =5000))
  
  
  FOC_p.post <- function(innitial_vetor){
    len <- length(innitial_vetor)
    prices <- innitial_vetor[1:len]
    quality <- data.R22Q1$Averate2
    implied_shares <- calcShares.p(prices,quality,meanval,alpha,tau)
    price_over_shares <- matrix(1 / (implied_shares)) %*% matrix(prices, nrow = 1)
    elasticities_pre_price <- elast_price(implied_shares,prices,alpha)
    derivatives_price <- elasticities_pre_price / price_over_shares
    
    # markups_post <- c(-solve(t(derivatives_price) * ownerpre) %*% implied_shares)
    marg_cost <- calcMc_price.p(price_pre,quality_pre,meanval,alpha,tau,ownerpre)
    
    # quality_over_shares <- matrix(1 / implied_shares) %*% matrix(quality, nrow = 1)
    # elasticities_pre_quality <- elast_quality(implied_shares,quality)
    # derivatives_quality <- elasticities_pre_quality / quality_over_shares
    
    # markups_post <- c(-solve(t(derivatives_quality) * ownerpre) %*% implied_shares)
    # vec1 <- as.matrix(-0.4410*quality+Unobpart)
    M1_PRICE <- t(derivatives_price) * ownerpost
    # M2_QUALITY <- t(derivatives_quality) * ownerpre
    # Merge_matrix <- rbind(cbind(M1_PRICE,matrix(0,nrow=nrow(M1_PRICE),ncol=ncol(M2_QUALITY))),cbind(matrix(0,nrow=nrow(M2_QUALITY),ncol=ncol(M1_PRICE)),M2_QUALITY))
    price_mc <- prices - marg_cost
    # matrix_price_mc <- append(price_mc,price_mc)
    # matrix_price_mc <- matrix(matrix_price_mc,ncol = 1)
    # matrix_shares_mC <- append(implied_shares,-vec1)
    # matrix_shares_mC <- matrix(matrix_shares_mC,ncol = 1)
    thisFOC <- as.vector((implied_shares) + M1_PRICE %*% price_mc)
    return(thisFOC)
  }
  
  
  
  minResult.p.post <- dfsane(innitial_vector.p,FOC_p.post,quiet=FALSE,control=list(maxit = 5000))
  
  
  
  EstpricePre.p <- minResult.p.pre$par
  EstsharesPre.p <- calcShares.p(EstpricePre.p,data.R22Q1$Averate2,meanval,alpha,tau)
  EstpricePost.p <- minResult.p.post$par
  EstsharesPost.p <- calcShares.p(EstpricePost.p,data.R22Q1$Averate2,meanval,alpha,tau)
  
  Est_result.p <- data.frame(brand_pre,brand_post,EstpricePre.p,EstsharesPre.p,EstpricePost.p,EstsharesPost.p)
  Est_result.p$label <- ''
  Est_result.p$label[Est_result.p$brand_post=='irobot'] <- "*"
  Est_result.p$priceDif.p <- (Est_result.p$EstpricePost.p-Est_result.p$EstpricePre.p)/Est_result.p$EstpricePre.p
  Est_result.p$EstsharDif.p <- (Est_result.p$EstsharesPost.p-Est_result.p$EstsharesPre.p)/Est_result.p$EstsharesPre.p
  Est_result.p <- Est_result.p %>%
    relocate(label,.after = brand_post)
  stargazer(Est_result.p,type = 'text')
  
  
  Pro1 <- tibble(Est_result.pg,Est_result.p[,-c(1,2,3)])
  Pro1$Ob.price <- price_pre
  Pro1$Ob.quality <- quality_pre
  Pro1$Obprice_dif_pg <- price_pre-Pro1$EstpricePre.pg
  Pro1$Obprice_dif_p <- price_pre-Pro1$EstpricePre.p
  Pro1$Obquality_dif_pg <- quality_pre-Pro1$EstqualityPre.pg
  Pro1$Ob.shares <- exp(data.R22Q1$shares+log(0.5))
  shares_ori <- exp(data.R22Q1$shares+log(0.5))
  Pro1$EST_ob_sharepg <- Pro1$EstsharesPre.p-shares_ori
  
  
  Pro1 <- Pro1[order(Pro1$label,decreasing = T),]
  Pro1 <- Pro1[Pro1$label=='*',]
  addWorksheet(wb1,sheetName = market_ids)
  writeData(wb1,sheet = market_ids,x = Pro1)


}

saveWorkbook(wb1, "logit_P_increasing.xlsx", overwrite = TRUE)



